NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2020-05-26 Manuscript/manuscriptPGPE.tex
Update ECC-lipid results

      \begin{table*}[htb]
  %\begin{sidewaystable*}[!p]
  \centering
  \caption{List of MD simulations with PG lipids.
    % The salt concentrations calculated as [salt]=N$_{\rm c} \times$[water]\,/\,N$_{\rm w}$, where [water]\,=\,55.5~M.
    % these correspond the concentrations reported in the experiments by Akutsu et al.~\cite{akutsu81}.
    % The lipid force fields named as in our previous work~\cite{botan15}.
  }\label{systemsPG}
  \begin{minipage}[t]{\textwidth}
    \begin{tabular}{l c c r r r r r r c c}
      %\hline
      % some footnotes are not visible in typeset-MS (pdf)
      lipid/counter-ions & force field for lipids / ions & NaCl (M) &  \footnote{Number of lipid molecules with largest mole fraction}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$   & \footnote{Number of additional cations}N$_{\rm c}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns) & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns) &   \footnote{Reference for simulation files}files\\
      \hline
      POPG/K$^+$  & CHARMM36 \cite{??} \todoi{Correct citation for CHARMM POPG}    &0         & 118& 4110   &0    & 298  & 100 & 100 & \cite{CHARMM36popg}  \\
      POPG             & CHARMM36 \cite{??}        & 0.11           & 500 & 25000 & 49  &  310  & 500 & 100 & \cite{POPGcharmm150mMNaCl} \\
      POPG             & CHARMM36 \cite{??}        & 0              & 500 & 25000 & 0   &  310  & 500 & 100 & \cite{POPGcharmm} \\
      \hline
      POPG/Na$^+$  & Slipids / {\AA}qvist \cite{jambeck13,aqvist90}    &0         & 288 	& 10664   &0     & 298  & 250 & 100 & \cite{slipidsPOPGfiles} \\
      DPPG/Na$^+$  & Slipids / {\AA}qvist \cite{jambeck13,aqvist90}    &0         & 288 	& 11232  &0     & 314  & 200 & 100 & \cite{slipidsDPPGfiles} \\
      DPPG/Na$^+$  & Slipids / {\AA}qvist \cite{jambeck13,aqvist90}    &0         & 288 	& 11232   &0     & 298  & 400 & 100 & \cite{slipidsDPPGfilesT298K} \\
      POPG         & Slipids / {\AA}qvist \cite{jambeck13,aqvist90}    & 0    & 500 & 25000 & 0  &  310  & 500 & 100 & \cite{POPGslipids} \\
      POPG         & Slipids / {\AA}qvist \cite{jambeck13,aqvist90}    & 0.11    & 500 & 25000 & 49  &  310  & 500 & 100 & \cite{POPGslipids150mMNaCl} \\
      \hline
      POPG             & LIPID17 / Dang \cite{gould18,smith94}         & 0              & 500 & 25000 & 0   &  310  & 500 & 100 & \cite{POPGlipid17} \\
      POPG             & LIPID17 \cite{??}         & 0.11           & 500 & 25000 & 49  &  310  & 500 & 100 & \cite{POPGlipid17150mMNaCl} \\
      \hline
      POPG             & GROMOS-CKP \cite{??}         & 0              & 500 & 25000 & 0  &  310  & 500 & 100 & \cite{POPGgromosCKP} \\
      POPG             & GROMOS-CKP \cite{??}         & 0.11           & 500 & 25000 & 49 &  310  & 500 & 100 & \cite{POPGgromosCKP150mMNaCl} \\
    \end{tabular}
  \end{minipage}
  % \end{sidewaystable*}
    \todo{We need citations for the force fields.}
\end{table*}

@@

@@

      \hline
      POPC:POPG (4:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}   &0          & 0  & 350:88 & 26265 & 0  &  298  & 400 & 350 & \cite{Lipid17POPCPOPG8020} \\
      POPC:POPG (4:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 0.1& 350:88 & 26124 & 47 &  298  & 400 & 150 & \cite{Lipid17POPCPOPG8020100mMCaCl} \\
      POPC:POPG (4:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 1.0& 350:88 & 24840 & 475 &  298  & 1200 & 200 & \cite{Lipid17POPCPOPG80201000mMCaCl} \\
      POPC:POPG (1:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 0  & 150:150 & 31572 & 0  &  298  & 320 & 200 & \cite{Lipid17POPCPOPG5050} \\
      POPC:POPG (1:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}     &0          & 0.1& 150:150 & 31401 & 57 &  298  & 720 & 198 & \cite{Lipid17POPCPOPG5050100mMCaCl} \\
      POPC:POPG (1:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 1.0& 150:150 & 29865 & 569 &  298  & 720 & 200 & \cite{Lipid17POPCPOPG50501000mMCaCl} \\
      \hline
      POPC             & Berger \cite{??} \todoi{This is probable not plain berger, correct force filed should be described.}  &0  & 0  & 256 & 10240 & 0  &  300  & 300 & 200 & \cite{POPCberger300K} \\
      POPC:POPE (1:1)  & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.} &0          & 0  & 128 & 11008 & 0  &  300  & 300 & 200 & \cite{POPC1POPE1berger} \\
      POPC:DOPE (1:1)  & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.}         &0          & 0  & 128 & 10240 & 0  &  300  & 300 & 200 & \cite{POPC1DOPE1berger} \\
     \hline
      DOPC             & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.}         &0          & 0  & 256 & 11008 & 0  &  300  & 300 & 200 & \cite{DOPCberger300K} \\
      DOPC:DOPE (1:1)  & Berger \cite{??}   \todoi{This is probable not plain berger, correct force filed should be described.}        &0          & 0  & 128 & 11008 & 0  &  300  & 300 & 200 & \cite{DOPC1DOPE1berger} \\
    \end{tabular}
  \end{minipage}
  %\end{sidewaystable*}
  \todo{Data for POPC:POPG mixtures by listed by Antonio Peon is missing from this table} \\
    \todo{We need citations for the force fields.}
\end{table*}

>>>>

      \begin{table*}[htb]
  %\begin{sidewaystable*}[!p]
  \centering
  \caption{List of MD simulations with PG lipids.
    % The salt concentrations calculated as [salt]=N$_{\rm c} \times$[water]\,/\,N$_{\rm w}$, where [water]\,=\,55.5~M.
    % these correspond the concentrations reported in the experiments by Akutsu et al.~\cite{akutsu81}.
    % The lipid force fields named as in our previous work~\cite{botan15}.
  }\label{systemsPG}
  \begin{minipage}[t]{\textwidth}
    \begin{tabular}{l c c r r r r r r c c}
      %\hline
      % some footnotes are not visible in typeset-MS (pdf)
      lipid/counter-ions & force field for lipids / ions & NaCl (M) &  \footnote{Number of lipid molecules with largest mole fraction}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$   & \footnote{Number of additional cations}N$_{\rm c}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns) & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns) &   \footnote{Reference for simulation files}files\\
      \hline
      POPG/K$^+$  & CHARMM36 \cite{??} \todoi{Correct citation for CHARMM POPG}    &0         & 118& 4110   &0    & 298  & 100 & 100 & \cite{CHARMM36popg}  \\
      POPG             & CHARMM36 \cite{??}        & 0.11           & 500 & 25000 & 49  &  310  & 500 & 100 & \cite{POPGcharmm150mMNaCl} \\
      POPG             & CHARMM36 \cite{??}        & 0              & 500 & 25000 & 0   &  310  & 500 & 100 & \cite{POPGcharmm} \\
      \hline
      POPG/Na$^+$  & Slipids / {\AA}qvist \cite{jambeck13,aqvist90}    &0         & 288 	& 10664   &0     & 298  & 250 & 100 & \cite{slipidsPOPGfiles} \\
      DPPG/Na$^+$  & Slipids / {\AA}qvist \cite{jambeck13,aqvist90}    &0         & 288 	& 11232  &0     & 314  & 200 & 100 & \cite{slipidsDPPGfiles} \\
      DPPG/Na$^+$  & Slipids / {\AA}qvist \cite{jambeck13,aqvist90}    &0         & 288 	& 11232   &0     & 298  & 400 & 100 & \cite{slipidsDPPGfilesT298K} \\
      POPG         & Slipids / {\AA}qvist \cite{jambeck13,aqvist90}    & 0    & 500 & 25000 & 0  &  310  & 500 & 100 & \cite{POPGslipids} \\
      POPG         & Slipids / {\AA}qvist \cite{jambeck13,aqvist90}    & 0.11    & 500 & 25000 & 49  &  310  & 500 & 100 & \cite{POPGslipids150mMNaCl} \\
      \hline
      POPG             & LIPID17 / Dang \cite{gould18,smith94}         & 0              & 500 & 25000 & 0   &  310  & 500 & 100 & \cite{POPGlipid17} \\
      POPG             & LIPID17 \cite{??}         & 0.11           & 500 & 25000 & 49  &  310  & 500 & 100 & \cite{POPGlipid17150mMNaCl} \\
      \hline
      POPG             & GROMOS-CKP \cite{??}         & 0              & 500 & 25000 & 0  &  310  & 500 & 100 & \cite{POPGgromosCKP} \\
      POPG             & GROMOS-CKP \cite{??}         & 0.11           & 500 & 25000 & 49 &  310  & 500 & 100 & \cite{POPGgromosCKP150mMNaCl} \\
    \end{tabular}
  \end{minipage}
  % \end{sidewaystable*}
  \todo{Citations and ion model for CHARMM36?} \\
  \todo{Lipid17 simulation with correct dihedral potentials still coming.} \\
  \todo{Citation and ion model for GROMOS-CKP?}
\end{table*}

@@

      POPC                   & GROMOS-CKP / ?? \cite{??,??}  & 0         & 0  & 500     & 25000 & 0   &  310  & 500 & 100 & \cite{POPCgromosCKPT310K}  \\
      POPC:POPG (7:3)        & GROMOS-CKP / ?? \cite{??,??}  & 0         & 0  & 350:150 & 25000 & 0   &  310  & 500 & 100 & \cite{POPC7POPG3gromosCKPT310K} \\

@@

      \hline
      POPC:POPG (4:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}   &0          & 0  & 350:88 & 26265 & 0  &  298  & 400 & 350 & \cite{Lipid17POPCPOPG8020} \\
      POPC:POPG (4:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 0.1& 350:88 & 26124 & 47 &  298  & 400 & 150 & \cite{Lipid17POPCPOPG8020100mMCaCl} \\
      POPC:POPG (4:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 1.0& 350:88 & 24840 & 475 &  298  & 1200 & 200 & \cite{Lipid17POPCPOPG80201000mMCaCl} \\
      POPC:POPG (1:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 0  & 150:150 & 31572 & 0  &  298  & 320 & 200 & \cite{Lipid17POPCPOPG5050} \\
      POPC:POPG (1:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}     &0          & 0.1& 150:150 & 31401 & 57 &  298  & 720 & 198 & \cite{Lipid17POPCPOPG5050100mMCaCl} \\
      POPC:POPG (1:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 1.0& 150:150 & 29865 & 569 &  298  & 720 & 200 & \cite{Lipid17POPCPOPG50501000mMCaCl} \\
      \hline
      POPC             & Berger \cite{??} \todoi{This is probable not plain berger, correct force filed should be described.}  &0  & 0  & 256 & 10240 & 0  &  300  & 300 & 200 & \cite{POPCberger300K} \\
      POPC:POPE (1:1)  & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.} &0          & 0  & 128 & 11008 & 0  &  300  & 300 & 200 & \cite{POPC1POPE1berger} \\
      POPC:DOPE (1:1)  & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.}         &0          & 0  & 128 & 10240 & 0  &  300  & 300 & 200 & \cite{POPC1DOPE1berger} \\
     \hline
      DOPC             & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.}         &0          & 0  & 256 & 11008 & 0  &  300  & 300 & 200 & \cite{DOPCberger300K} \\
      DOPC:DOPE (1:1)  & Berger \cite{??}   \todoi{This is probable not plain berger, correct force filed should be described.}        &0          & 0  & 128 & 11008 & 0  &  300  & 300 & 200 & \cite{DOPC1DOPE1berger} \\
    \end{tabular}
  \end{minipage}
  %\end{sidewaystable*}
  \todo{New CHARMM simulations are still to be ran.} \\
  \todo{Citation and ion model for GROMOS-CKP?} \\
  \todo{Citation and description for ''Berger'' model?}
\end{table*}
